---
title: Rasterisation
runningheader: "Illustrating Raster Maps"
author: notes
date: "`r Sys.Date()`"
documentclass: book
bibliography: ../../bibliography/bibliography.bib
csl: ../../bibliography/cambridge-university-press-numeric.csl
link-citations: yes
classoption:
  - fleqn
extra_dependencies:
  - float
site: bookdown::bookdown_site
output:
  bookdown::tufte_book2
---



<!--- Global Settings --->
```{r include = FALSE}

# Settings
knitr::opts_chunk$set(echo = FALSE)
options(knitr.table.format = 'latex')
options(knitr.kable.NA = '')

# Invalidate cache when the tufte version changes
library(tufte)
knitr::opts_chunk$set(cache.extra = packageVersion(pkg = 'tufte'))
options(htmltools.dir.version = FALSE)
```


```{r include = FALSE}
library(xtable)
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)

library(magrittr)
library(latex2exp)
library(patchwork)
library(knitr)
library(kableExtra)

library(tmap)
library(sf)

```

<!--- settings --->
```{r exploration settings}
pathstr <- dirname(getwd())
```

<!--- functions --->
```{r exploration functions}
sys.source(file = file.path(pathstr, 'rasterisation', 'Raw.R'), envir = knitr::knit_global())
sys.source(file = file.path(pathstr, 'rasterisation', 'Projected.R'), envir = knitr::knit_global())
```

# *INTRODUCTION* {-}

A brief text, program, about rasterisation for geospatial analysis, statistics, or modelling.


# *Projecting*

For ...

## Unprojected Map

```{r}
raw <- Raw()
projected <- Projected(blob = raw$blob)
```

This example illustrates the Open Street Map (OSM) bicycle hire data. Its Geographic Co$\ddot{o}$rdinate System is `r raw$properties$input`

```{r, fig.align = 'center', fig.height = 3, fig.cap = "An illustration of bicycle hiring points across London, United Kingdom.  It is an unprojected map, the geographic coordinate system is ..."}
raw$diagram
```


## Projected Map

The projected form has co$\ddot{o}$rdinate reference system `r projected$properties$input`

<!--- diagram --->
```{r, fig.align = 'center', fig.height = 3, fig.cap = "An illustration of bicycle hiring points across London, United Kingdom; projected."}
projected$diagram
```






